Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-01 Documents/Paper/ms.tex
Challenges figure

Diffusive Nested Sampling
\citep[DNS][]{dnest} replaces the posterior distribution with an alternative target
distribution composed of a mixture of the prior distribution with other, more
constrained versions of the prior, facilitating mixing between the multiple modes
and along degeneracy curves.
This is similar to the idea of annealed importance sampling
\citep{neal} or parallel tempering \citep{pt},
where the target distribution is modified from the posterior to something
``easier''. However,
the sequence of distributions used in Nested Sampling avoids some of the
problems with annealing-based methods. In particular, there is no need to choose
a temperature schedule (a potentially large set of tuning parameters),
and the method does not fail when phase transitions
are present.

>>>>

\begin{figure}
\begin{minipage}[lr]{\textwidth}
\begin{center}
\includegraphics[width=2.7in]{challenges.pdf}
\includegraphics[width=2.7in]{dnest.png}
\end{center}
\end{minipage}
\caption{{\bf Left}: An example of a two-dimensional posterior distribution
with multiple modes, strong dependence, and a phase transition (in the top
right mode). While this low dimensional example is not difficult to sample,
an analogous problem in high dimensions would be. {\bf Right}: Diffusive
Nested Sampling replaces the target posterior distribution by a mixture of
constrained priors. The density is non-negligible everywhere (since the prior
is a component of this distribution), and states intermediate between the two
phases in the top-right mode are appropriately up-weighted.
\label{fig:challenges}}
\end{figure}

Diffusive Nested Sampling
\citep[DNS][]{dnest} replaces the posterior distribution with an alternative target
distribution composed of a mixture of the prior distribution with other, more
constrained versions of the prior, facilitating mixing between the multiple modes
and along degeneracy curves.
This is similar to the idea of annealed importance sampling
\citep{neal} or parallel tempering \citep{pt},
where the target distribution is modified from the posterior to something
``easier''. However,
the sequence of distributions used in Nested Sampling avoids some of the
problems with annealing-based methods. In particular, there is no need to choose
a temperature schedule (a potentially large set of tuning parameters),
and the method does not fail when phase transitions
are present.
Figure~\ref{fig:challenges} shows a mock-up of a two dimensional posterior
density with three modes, one of which contains a strong dependence, and
another of which contains a phase transition.
